### 2010-12-09 docs/tex/signature.tex
Title date time updated

\begin{flushright}
\begin{minipage}{8cm}
\rule{5cm}{0.1mm} Chair\\[0.4cm]
\rule{5cm}{0.1mm} Examiner\\[0.4cm]
\rule{5cm}{0.1mm} Examiner\\[0.4cm]
\rule{5cm}{0.1mm} Supervisor\\[0.8cm]
\end{minipage}
\end{flushright}
\makebox[4cm][l]{Approved by} \rule{10cm}{0.1mm}\\ 
\makebox[4cm][l]{} Chair of Department or Graduate Program Director\\[1cm]
\makebox[4cm][l]{\rule{2cm}{0.1mm} 20 \rule{1cm}{0.1mm}} \rule{10cm}{0.1mm}\\ 
\makebox[4cm][l]{} Dean of Faculty

>>>>

\begin{flushright}
\begin{minipage}{10cm}
\rule{7cm}{0.1mm} Chair\\[0.4cm]
\rule{7cm}{0.1mm} Examiner\\[0.4cm]
\rule{7cm}{0.1mm} Examiner\\[0.4cm]
\rule{7cm}{0.1mm} Supervisor\\[0.8cm]
\end{minipage}
\end{flushright}
\makebox[5cm][l]{Approved by} \rule{10cm}{0.1mm}\\ 
\makebox[5cm][l]{} Chair of Department or Graduate Program Director\\[1cm]
\makebox[5cm][l]{\rule{3cm}{0.1mm} 20 \rule{1cm}{0.1mm}} \rule{10cm}{0.1mm}\\ 
\makebox[5cm][l]{} Dean of Faculty
